Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions

### 2023-01-26 manuscript.Rmd
Update manuscript.Rmd

```{r set-up, include = FALSE}
library(knitr)
library(bookdown)
library(officedown)
library(officer)
library(tidyverse)
library(flextable)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  dpi = 50
  )
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 11
  )
```

@@

Soil of the three substrates was analyzed for the fraction \< 2mm fraction. Soil texture was classified according to the *Bodenkundliche Kartieranleitung* [@BodenkundlKartieranl.2005]. The pH was measured in CaCl~2~ solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract. For calculating CaCO~3~, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33. To calculate total N and the C/N ratio, a subsample was ashed at 1000 °C.

@@

```{r figure-map, fig.cap = "Map"}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

@@

```{r figure-effects, fig.cap = "Effects"}
knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r figure-persistence, fig.cap = "Persistence"}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)"}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "Recovery"}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-nmds, fig.cap = "NMDS"}
knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```

>>>>

```{r set-up, include = FALSE}
library(knitr)
library(bookdown)
library(officedown)
library(officer)
library(tidyverse)
library(flextable)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  dpi = 300,
  fig.cap = FALSE
  )
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 11
  )
```

@@

Soil of the three substrates was analyzed for the fraction \< 2mm fraction. Soil texture was classified according to the *Bodenkundliche Kartieranleitung* [@BodenkundlKartieranl.2005]. The pH was measured in CaCl~2~ solution. Plant available phosphorus and potassium were measured in a calcium acetate-lactate extract and magnesium in CaCl~2~ extract. For calculating CaCO~3~, a subsample was annealed at 550 °C and the measured C amount calculated with 8.33. To calculate total N and the C/N ratio, a subsample was incinerated at 1000 °C.

@@

```{r figure-map, fig.cap = "Map", fig.asp = 0.7272}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

The experiment was located

@@

```{r figure-effects, fig.cap = "Effects", fig.asp = 3.3}
knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r figure-persistence, fig.cap = "Persistence", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "Recovery", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-nmds, fig.cap = "NMDS", fig.asp = 1.0312}
knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```
